---
title: "Home Prices and BART Commute Times"
author: "Garret Christensen"
date: "April 1, 2016"
output: html_document
---

```{r}
data<-read.csv("BART.csv")
mod1<-lm(pricepersqft~commute, data = data)
data$commute_sq=data$commute*data$commute
mod2<-lm(pricepersqft~commute+commute_sq, data=data)
```

A real estate website [estately](http://www.estately.com/bay-area-home-affordability-transit-stop) calculated the average price per square foot of houses in the mile around each BART station, and also listed a few commute times to downtown SF (Embarcadero). I figured that meant I needed to run some regressions.

```{r, results='asis', message=FALSE}
plot(pricepersqft~commute, data=data)
abline(mod1)
library(stargazer)
stargazer(mod1, mod2, se=list(NULL, NULL), type="html", out="stargazerout.html", title="Home Prices and BART Commutes", align=TRUE, column.labels=c("Linear","Quadratic"))
```


That means every minute on BART is associated with $12.78 per square foot cheaper house. All the usual caveats: only on average, it's not causal, etc. etc. Also, there's a statistically significant quadratic relationship, but the difference in the relevant region isn't enormous. If you can't read a regression table, what we're looking at is:

$$price=900-12.78*commute$$
$$price=1043-28.89*commute+.317*commute^2$$

Still, I think that's sort of neat. What's neater is R Markdown, R projects, and how version control is seemlessly built into R Studio. That is *smooth*. The code for this is on [Github](http://www.github.com/garretchristensen/BARTprices).
