---
title: "Home Prices and BART"
author: "Garret Christensen"
date: "April 1, 2016"
output: html_document
---

```{r}
data<-read.csv("BART.csv")
mod1<-lm(pricepersqft~commute, data = data)
data$commute_sq=data$commute*data$commute
mod2<-lm(pricepersqft~commute+commute_sq, data=data)
```

A real estate website [estately](http://www.estately.com/bay-area-home-affordability-transit-stop) calculated the average price per square foot of houses in the mile around each BART station, and also listed a few commute times to downtown SF (Embarcadero). I figured that meant I needed to run some regressions.

```{r, results='asis', message=FALSE}
plot(pricepersqft~commute, data=data)
abline(mod1)
library(stargazer)
stargazer(mod1, mod2, se=list(NULL, NULL), type="html", out="stargazerout.html", title="Home Prices and BART Commutes", align=TRUE, column.labels=c("Linear","Quadratic"))
```


I think that's sort of neat. What's neater is R Markdown, R projects, and how version control is seemlessly built into R Studio. That is *smooth*. The code for this is on Github.
